---
title: "RStudio Addin Overview"
author: ""
date: ""
output: 
   html_document:
      css: ["rstudioaddin.css"]
description: "How to build a quick RStudio Addin"
---

My quick example of building the Addin is taken from materials on [RStudio Addins](https://rstudio.github.io/rstudioaddins/?msclkid=49f8bd61c69211ecbafd6ee106d2b8d6)

## There are two major types of Addins:

* Text macros - Either insert text into the console/script or transform text within the console/script pane. 
  + styler example
  + Simple and contrived example

* Shiny Gadgets -fully interactive Shiny applications. Gadgets may also perform text transformations but they are of course capable of much more.
  + timber will use this type of Shiny Gadget Addin

## Simple and Contrived Example

We want to have an easy way to insert `%in%` as doing `Shift+5` is hurting our hands.  `%in%` is used to identify if an element belongs to a vector.

```{r}
"p" %in% c("r", "s", "t")
```

We can create an RStudio Addin to help us build a quick way to insert `%in%` into our script.  To manipulate the RStudio environment, we will make use of the package [rstudioapi](https://rstudio.github.io/rstudio-extensions/rstudioapi.html), to get under the hood of RStudio.  A great package, but could be an entire presentation - make sure to check it out!

Two simple folders in our directory with two simple files will get us up and running in no time!

* `R/insertInAddin.R`
* `inst/rstudio/addins.dcf`

```{r, eval=FALSE, echo=TRUE,  verbatim = TRUE, message = FALSE}
insertInAddin <- function() {
  rstudioapi::insertText(" %in% ")
}
```

<p></p>
```{r, eval=FALSE, echo=TRUE, verbatim = TRUE, message = FALSE}
Name: Insert %in%
Description: Inserts `%in%` at the cursor position.
Binding: insertInAddin
Interactive: false
```
