---
title: "RStudio Addin Overview"
author: "Ben Straub"
date: "`r Sys.Date()`"
output: 
   html_document:
      css: ["rstudioaddin.css"]
description: "How to build a quick RStudio Addin"
---

These materials are drawn from [RStudio Addins](https://rstudio.github.io/rstudioaddins/?msclkid=49f8bd61c69211ecbafd6ee106d2b8d6)

There are two major types of addins:

Text macros, which insert text into the console or source pane and in some cases transform text within the source pane. The insertInAddin addin defined above is an example of a text macro.

Shiny Gadgets, which are fully interactive Shiny applications. Gadgets may also perform text transformations but they of course capable of much more.

More details on Shiny Gadgets are provided below, but first we’ll take a look at using the rstudioapi package (which allows us to interact with RStudio from R code) and then what it takes to install and register an addin


```{r, warning=FALSE, results='hold'}


```

```{r, warning=FALSE, results='hold'}


```